---
title: "LIMA, PAUL CARLOS I T - FA7"
author: "Paul Carlos T. Lima I"
date: "2023-04-19"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FA7 ANSWERS by Lima

#### 1. A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

#### (a)Calculate the probability that a memory stick will be scrapped.

#### (b)Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance.

**For (a)**

To calculate the probability that a memory stick will be scrapped, we can use the function "punif()" in R, which calculates the CDF for a uniform distribution. Hence in R Format it would be:

R Code:

```{r 1A}

# FOR 1A
# Specify the range of the Memory Stick Lengths
MStick_MinL <- 2
MStick_MaxL <- 12

# Compute for the probability that a memory stick will be scrapped
Prob_Scrapped <- 1 - punif(10, MStick_MinL, MStick_MaxL)
cat("Thus, the probability of memory stick being scrapped is:", Prob_Scrapped, "\n")

```

**For (b)**\
There are 3 things need to be done: 1. Simulate 50 memory stick lengths.\
2. Obtain a histogram of the simulated values.\
3. Calculate the simulated mean and variance.\
In R Format it would be:

R Code:

```{r 1B}

# FOR 1B
# Specify the range of the Memory Stick Lengths
MinL <- 2
MaxL <- 12

# Simulate the 50 Memory Stick Lengths needed
S_Lengths <- runif(50, MinL, MaxL)

# Create a HISTOGRAM of the Simulated Memory Stick Lengths
hist(S_Lengths, main = "Simulated Memory Stick Lengths", xlab = "Length", ylab = "Frequency")

# Calculate the Mean and Variance of the Simulated Memory Stick Lengths 
SL_Mean <- mean(S_Lengths)
cat("The Mean of the Simulated Memory Stick Lengths is:", SL_Mean, "\n", "\n")

SL_Variance <- var(S_Lengths)
cat("The Variance of the Simulated Memory Stick Lengths is:", SL_Variance, "\n")

```

#### **2. Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf**

#### **f(x) = 0.025x + b, 2 \< x \< 6**

#### **(a) Show that, for this to be a genuine probability density, b = 0.15.**

#### **(b) Find the probability that the measurement of the current exceeds 3.**

#### **(c) Find E(X).**

**For (a)**\
To show that, for the pdf function to be a genuine probability density, b = 0.15. We need to satisfy the 3 conditions of the PDF.\
\
1. The pdf must be non negative .\
f(x) â‰¥ 0\
\
2. the area under the curve of f(x) between two points a and b is the probability that the random variable X lies between a and b.

b\
âˆ« f(x)dx = P(a â‰¤ X â‰¤ b)]\
a

3\. The integral of the pdf over its entire domain must be equal to 1. âˆž âˆ« f(x)dx = 1 âˆ’âˆž

In R Format it would be:

R Code:

```{r 2A}

# FOR 2A
# Define the given function
b <- 0.15
PD_Function_2A <- function(x) {0.025 * x + b}

# Calculate the integral of the function over the interval from 2 to 6
IResult2A <- integrate(PD_Function_2A, 2, 6)

# Use the $value, a class of "integrate" to extract the numerical value of the result
Genuine_PD <- IResult$value

cat("Since the pdf passes the 3 criterion with the pdf being non-negative for all values of x within its domanin, and the entire domain is equal to:", Genuine_PD, "\n", "\n", "Thus it is a genuine probability density when b = 0.15." )
```

**For (b)**

To find the probability that the measurement of the current exceeds 3.

Using R Language it would be:

R Code:

```{r 2B}

# FOR 2B
# Define the given function with the calculated value of b = 0.15
PD_Function_2B <- function(x) {0.025 * x + 0.15}

# Calculate the integral of the pdf over the interval from 3 to 6
IResult2B <- integrate(PD_Function_2B, 3, 6)

# Use the $value, a class of "integrate" to extract the numerical value of the result
Prob_Exceed_3 <- IResult2B$value

cat("The probability that the measurement of the current exceeds 3 is:", Prob_Exceed_3, "\n")
```

**For (c)**

To find E(X).

Using R Language it would be:

R Code:

```{r 2C}

# FOR 2C
# Define the given function with the calculated value of b = 0.15
PD_Function_2C <- function(x) {0.025*x + 0.15}

# Specify the integration limits for the integral
Lower_Value <- 2
Upper_Value <- 6

# Define the integrand for E(X)
integrand <- function(x) {x * PD_Function_2C(x)}

# Calculate the expected value using the integrate function
# And use the $value, a class of "integrate" to extract the numerical value of the result
E_X <- integrate(integrand, Lower_Value, Upper_Value)$value

cat("Thus, E(X) =", E_X, "\n")
```

#### **3.** In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in [-ðœ‹,ðœ‹]. Find P(X â‰¤ 0) and P(X â‰¤ ðœ‹/2) using R Language.

To Find P(X â‰¤ 0) and P(X â‰¤ ðœ‹/2) using R Language.

Using R Language it would be:

R Code:

```{r 3}

# FOR 3
# Define the Range of the UD (Uniform Distribution)
UDRange_Min <- -pi
UDRange_Max <- pi

# Calculate P(X â‰¤ 0) and P(X â‰¤ ðœ‹/2)

# FOR P(X â‰¤ 0)
Prob_Less_0 <- punif(0, UDRange_Min, UDRange_Max)

# FOR P(X â‰¤ ðœ‹/2)
Prob_Less_Pi_Over_2 <- punif(pi/2, UDRange_Min, UDRange_Max)


cat("Thus, \n \n P(X â‰¤ 0) =", Prob_Less_0, "\n", "\n", "P(X â‰¤ ðœ‹/2) =", Prob_Less_Pi_Over_2)

```
